animbook: Visualizing changes in performance measures and demographic affiliations using animation

### 2024-02-08 animbook-journal.Rmd
discussion

  There are some potential new directions to develop this work. Some applications might benefit by re-parameterization of the x-axis from years to ages (e.g. company ages, time since the company was founded). One could also re-arrange the mapping of variables to the plot and animations. For example, the New York Times article, mentioned that to better compare distributions in time, one could plot the quantiles, which would form something like an S-curve, and animate over time, to observe how the distributions are changing.

>>>>

  There are some potential new directions to develop this work. Some applications might benefit by re-parameterization of the x-axis from years to ages (e.g. company ages, time since the company was founded). This can be done by pre-processing before passing to animbook, but it would be more convenient to automate for the user. One could also imagine re-arranging the mapping of variables to the plot and animations, particularly, split on time, and animate on the quantiles to focus on movement through the ranks. The New York Times article had examples of this idea. The static funnel web plot is a good place to experiment with this, and to further enhance visually.
